An Embedding Framework for Consistent Polyhedral Surrogates

### 2019-05-22 neurips-19/poly-embed.tex
Proofreading edits

\bo{The following is not ideal because everywhere else in the paper, we always use $\R$ with $\gamma$ and $\reals^d$ with $\Gamma$}
\begin{definition}[Property, level set]\label{def:property}
  A \emph{property} is a function $\Gamma:\simplex\toto\R$.
  The \emph{level set} of $\Gamma$ for report $r$ is the set $\Gamma_r := \{p : r \in \Gamma(p)\}$.
\end{definition}

@@

\subsection{Inconsistency of top-$k$ losses}

Yang and Koyejo~\cite{yang2018consistency} prove the inconsistency of a family of polyhedral surrogates for the top-$k$ classification problem.
We are also able to show inconsistency using our embedding framework.
\jessie{Add sentence on what top-k problem is intuitively.}

@@

Yang and Koyejo~\cite{yang2018consistency} create a new surrogate loss that is consistent for the top-$k$ problem, but it should be noted that their surrogate is not convex.
Additionally, they evaluate two losses given by Lapin et al.~\cite{lapin2016loss, lapin2018analysis}, one of which is shown to be convex, but their consistency is left as an open question.
Following the notation of Yang, we call Lapin's~\cite{lapin2018analysis} convex surrogate $L_2$, and primarily focus on this.
Here, we assume $r \subseteq [n]$ and $k \leq n$ is a constant.

Our embedding framework can help lead us to distributions where the surrogate loss is not minimized by predicting the minimizer of $\ell_{top-k}$.
First, we want to show that for all $p \in \simplex$, there (1.) is some $u \in \{0,1\}^n$ that minimizes $\inprod{p}{L_2(\cdot)}$.
Then, we show (2.) there is a discrete loss $\ell_2$ that is embedded by $L_2$, where the embedded reports are the corners of the $n$-dimensional hypercube.
For $k=1$, we know that the $\ell_{top-k}$ reduces to 0-1 loss, so finally, we (3.) characterize the distributions where $\risk{L_2}(p) = \risk{\ell_2}(p) \neq \risk{\ell_{top-k}}(p)$.

@@

Now, for example, consider the surrogate discussed by Lapin et al.~\cite{yang2018consistency}, and Yang and Koyejo~\cite{yang2018consistency}.
We write the surrogate $L_2(u,y) := \max\left( \frac{1}{k} \sum_{i=1}^k (u + \indopp(y))_{[i]} - u_y \right)_+ $, where $\indopp(y) = \ones - e_y$, and $(x)_{[i]}$ is the $i^{th}$ largest component of $x$.

Consider the following process:  (1.) For all $p \in \simplex$, we can show that there is some $u \in \{0,1\}^n$ such that $u \in \argmin_{u'} \inprod{p}{L_2(u')}$.
(2.) Now consider the discrete loss
\begin{align*}
\ell_2(r,y) &= \Ind[y \not\in r] + \min\left(\frac{|r \setminus \{y\}|}{k}, 1\right)
\end{align*}
We claim that $L_2$ embeds $\ell_2$.  
(3.) Finally, taking $k = 1$, we see that $0 \in \argmin_{r' \subseteq [n]} \inprod{p}{\ell_2(r')}$ for any $p$ such that $\max_y p_y \leq 1/2$.

>>>>

\bo{The following is not ideal because everywhere else in the paper, we always use $\R$ with $\gamma$ and $\reals^d$ with $\Gamma$}
\begin{definition}[Property, level set]\label{def:property}
  A \emph{property} is a function $\Gamma:\simplex\toto\U$.
  The \emph{level set} of $\Gamma$ for report $u$ is the set $\Gamma_u := \{p : u \in \Gamma(p)\}$.
\end{definition}

@@

\subsection{Inconsistency of top-$k$ losses}
~\citet{lapin2016loss, lapin2018analysis}, provide two surrogate losses for measuring top-$k$ error, one of which is shown to be convex, but their consistency is left as an open question.

@@

Yang and Koyejo~\cite{yang2018consistency} create a new surrogate loss that is consistent for the top-$k$ problem, but it should be noted that their surrogate is not convex.
They also show that Lapin's surrogates are not consistent, but in a different manner than we do.
Following the notation of Yang, we call Lapin's~\cite{lapin2018analysis} convex surrogate $L_2$, and focus on this.
Here, we assume $r \subseteq [n]$ and $k \leq n$ is a constant.

Our embedding framework can help us find distributions where the surrogate loss is not minimized by predicting the minimizer of $\ell_{top-k}$.
First, we want to show that for all $p \in \simplex$, there (1.) is some $u \in \{0,1\}^n$ that minimizes $\inprod{p}{L_2(\cdot)}$.
Then, we show (2.) there is a discrete loss $\ell_2 : \{0,1\}^n \to \reals^Y_+$ that is embedded by $L_2$.  %, where the embedded reports are the corners of the $n$-dimensional hypercube.
For $k=1$, we know that the $\ell_{top-k}$ reduces to 0-1 loss, so finally, we (3.) characterize the distributions where $\risk{L_2}(p) = \risk{\ell_2}(p) \neq \risk{\ell_{top-k}}(p)$.

@@

We write the surrogate $L_2(u,y) := \max\left( \frac{1}{k} \sum_{i=1}^k (u + \indopp(y))_{[i]} - u_y \right)_+ $, where $\indopp(y) = \ones - e_y$, and $(x)_{[i]}$ is the $i^{th}$ largest component of $x$.

When embedding, we consider the discrete loss
\begin{align*}
\ell_2(r,y) &= \Ind[y \not\in r] + \min\left(\frac{|r \setminus \{y\}|}{k}, 1\right)~,~
\end{align*}
and claim that $L_2$ embeds $\ell_2$.  
(3.) Finally, taking $k = 1$, we see that $0 \in \argmin_{r' \subseteq [n]} \inprod{p}{\ell_2(r')}$ for any $p$ such that $\max_y p_y \leq 1/2$.
